25 years of Social Work Research

### 2015-02-21 dataCleaning.Rmd
Updated instructions.

Social work research can be really:  Bad
Social work research can be really: Bad
Social Work research can be really: bad
Social work research can be really: Bad
Social work research can be really: bad

Social Work research can be really:  bad

>>>>

Social work research can be really:  Bad
Social work research can be really: Bad
Social Work research can be really: bad
Social work research can be really: Bad
Social work research can be really: bad
Social Work research can be really:  bad

5.  Do necessary search and replace of subsequent code to get it working with the fully appended data file.
